---
title: "cinf401-assignment-2"
author: "Tram Nguyen"
date: "1/31/2018"
output: html_document
---

1. a line plot of the most commonly clicked classes over time (in either Industry or Technology taxonomy), x-axis: time (weeks), y-axis: number of clicks per class, use color for the class.
? either Industry or Technology? Do we need to separate these 2 terms?
```{r}
p <- read.csv(file="/bigdata/data/aaai/click-classes.csv", header=FALSE, sep=",")
colnames(p) <- c("ts","URL","keywords","classes")

# separate out ","
classes <- strsplit(as.character(p$classes), split=";")
p2 <- data.frame(ts=rep(p$ts, sapply(classes, length)),
                     Technology=unlist(classes))
p2$name <- p2$Technology
p2$name <- substr(p2$name,0,3)

#data frame of Industry
p2_industry <- p2[p2$name=="Ind",]
classes2 <- strsplit(as.character(p2_industry$Technology), split="\\|")
p3_industry <- data.frame(ts=rep(p2_industry$ts, sapply(classes2, length)),
                    Technology=unlist(classes2))
p3_industry$Technology <- factor(p3_industry$Technology, levels=sort(unique(p3_industry$Technology), decreasing=TRUE))
p3_industry <- p3_industry[p3_industry$Technology != "Information Technology",]
p3_industry <- p3_industry[p3_industry$Technology != "Artificial Intelligence",]
p3_industry <- p3_industry[p3_industry$Technology != "Technology",]
p3_industry <- p3_industry[p3_industry$Technology != "Industry",]

library(anytime)
p3_industry$Date <- anydate(p3_industry$ts)
p3_industry <- p3_industry[order(p3_industry$ts),]
p3_industry$week <- as.numeric(p3_industry$Date-p3_industry$Date[1]) %/% 7

p3_industry <- p3_industry[p3_industry$week != 27,]
p3_industry <- p3_industry[p3_industry$week != 29,]

click_per_week_industry <- aggregate(ts ~ week , p3_industry, length)
colnames(click_per_week_industry) <- c("week","click_per_week")

p3_industry <- merge(p3_industry, click_per_week_industry, "week")

ts_tech_industry <- aggregate(ts ~ week + Technology + click_per_week, p3_industry, length)
colnames(ts_tech_industry) <- c("week", "Technology","click_per_week", "Count")
ts_tech_industry$Percent <- ts_tech_industry$Count / ts_tech_industry$click_per_week

p_top_tech_industry <- aggregate(ts ~ Technology, p3_industry, length)
colnames(p_top_tech_industry) <- c("Technology", "Count")

#top count for each Tech in general
p_top_tech_industry <- p_top_tech_industry[order(-p_top_tech_industry$Count),]

#calculating the most common average 
p_avg_tech_industry <- aggregate(Percent ~ Technology, ts_tech_industry, mean)
p_avg_tech_industry <- p_avg_tech_industry[order(-p_avg_tech_industry$Percent),]
p_avg_tech_industry <- p_avg_tech_industry[1:6,]

#separate out "\\"
classes2 <- strsplit(as.character(p2_industry$Technology), split="\\|")
p3_industry <- data.frame(ts=rep(p2_industry$ts, sapply(classes2, length)),
                    Technology=unlist(classes2))
p3_industry$Technology <- factor(p3_industry$Technology, levels=sort(unique(p3_industry$Technology), decreasing=TRUE))

#Omitted common terms like "Industry", "Technology", "Information Technology", "AI"
p3_industry <- p3_industry[p3_industry$Technology != "Information Technology",]
p3_industry <- p3_industry[p3_industry$Technology != "Artificial Intelligence",]
p3_industry <- p3_industry[p3_industry$Technology != "Technology",]
p3_industry <- p3_industry[p3_industry$Technology != "Industry",]

#omitted the last 2 weeks since there's an error with the server
#p3 <- p3[p3$week != 27,]
#p3 <- p3[p3$week != 29,]


```

Graph of Industry count
```{r}
library(ggplot2)
p_common_clicked_avg_industry <-
  ggplot(ts_tech_industry[ts_tech_industry$Technology %in% c("Deep Learning", as.character(p_avg_tech_industry$Technology)),]) +
  geom_smooth(aes(x=week, y=Count, color=Technology), se=FALSE) +
  scale_x_continuous("Week",breaks=seq(0,26,2)) +
  scale_y_continuous("times clicked") +
  labs(color="") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank())
ggsave("tram-common-industry.png",p_common_clicked_avg_industry , width=6, height=6, dpi=600)
print(p_common_clicked_avg_industry)
```


Technology

```{r}
p2_tech <- p2[p2$name=="Tec",]
classes3 <- strsplit(as.character(p2_tech$Technology), split="\\|")
p3_tech <- data.frame(ts=rep(p2_tech$ts, sapply(classes3, length)),
                    Technology=unlist(classes3))
p3_tech$Technology <- factor(p3_tech$Technology, levels=sort(unique(p3_tech$Technology), decreasing=TRUE))
p3_tech <- p3_tech[p3_tech$Technology != "Information Technology",]
p3_tech <- p3_tech[p3_tech$Technology != "Artificial Intelligence",]
p3_tech <- p3_tech[p3_tech$Technology != "Technology",]
p3_tech <- p3_tech[p3_tech$Technology != "Industry",]

p3_tech$Date <- anydate(p3_tech$ts)
p3_tech <- p3_tech[order(p3_tech$ts),]
p3_tech$week <- as.numeric(p3_tech$Date-p3_tech$Date[1]) %/% 7

p3_tech <- p3_tech[p3_tech$week != 27,]
p3_tech <- p3_tech[p3_tech$week != 29,]

click_per_week_tech <- aggregate(ts ~ week , p3_tech, length)
colnames(click_per_week_tech) <- c("week","click_per_week")

p3_tech <- merge(p3_tech, click_per_week_tech, "week")

ts_tech <- aggregate(ts ~ week + Technology + click_per_week, p3_tech, length)
colnames(ts_tech) <- c("week", "Technology","click_per_week", "Count")
ts_tech$Percent <- ts_tech$Count / ts_tech$click_per_week

p_top_tech <- aggregate(ts ~ Technology, p3_tech, length)
colnames(p_top_tech) <- c("Technology", "Count")

#top count for each Tech in general
p_top_tech <- p_top_tech[order(-p_top_tech$Count),]

#calculating the most common average 
p_avg_tech <- aggregate(Percent ~ Technology, ts_tech, mean)
p_avg_tech <- p_avg_tech[order(-p_avg_tech$Percent),]
p_avg_tech <- p_avg_tech[1:6,]
```

Graph of Technology count
```{r}
p_common_clicked_avg_tech <-
  ggplot(ts_tech[ts_tech$Technology %in% c("Deep Learning", as.character(p_avg_tech$Technology)),]) +
  geom_smooth(aes(x=week, y=Count, color=Technology), se=FALSE) +
  scale_x_continuous("Week",breaks=seq(0,26,2)) +
  scale_y_continuous("times clicked") +
  labs(color="") +
  theme_bw() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank(),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank())
ggsave("tram-common-tech.png",p_common_clicked_avg_tech , width=6, height=6, dpi=600)
print(p_common_clicked_avg_tech)
```


2. a bar chart of the top classes overall, x-axis: class, y-axis: percent of overall clicks.

```{r}
#basic bar plot of Industry 
library(stringr)
bar_industry <- 
  ggplot(ts_tech_industry[ts_tech_industry$Technology %in% c("Deep Learning",as.character(p_avg_tech_industry$Technology)),],aes(x=Technology, y=Percent)) +
  geom_bar(stat="identity")+
  scale_x_discrete(labels = function(x) str_wrap(x, width = 10)) + 
  scale_y_continuous("Percent clicked") + 
  labs(color="blue") +
  theme_bw()
print(bar_industry)
```


